Figures and Tables

### 2020-09-28 paper/figures_tables.Rmd
Movement rates

>>>>

Movement rates, from Kimberly's paper, is the average number of meters moved per minute over the entire tracking period

```{r}
newpointlocs %>% 
  group_by(id, burst) %>% 
  summarise(rate = mean(mpm)) %>% 
  ggplot(., aes(x = rate)) +
  facet_wrap(~id, nrow = 3)+
  #geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = rate, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.055) +
  labs(title = "Movement rates") +
  theme_classic()

Important to keep in mind I could do movement rates or net squared displacement.

# I just added this. If I wanted to work with movement rates instead: which are the average number of meters moved over the tracking period. I consider period here as the burst. But I am also unclear about what the entire tracking period is here.

newpointlocs %>% 
# mydata %>%
#   add_count(Bird_ID) %>%
  group_by(id, burst) %>% 
  summarise(mov_rate = mean(mpm)) %>% 
  add_count(id) -> mov_rate_test

mov_rate_test %>% 
  ggplot(., aes(x = id, y = mov_rate)) +
  geom_boxplot()

mov_rate_test %>% 
  ggplot(., aes(x = mov_rate, group = id)) +
  facet_wrap(~id) +
  geom_density()

mov_rate_test %>%
  ggplot(., aes(x = mov_rate)) +
  geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mov_rate, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  #ylim(0, 0.055) +
  labs(title = "Movement rate") +
  theme_classic()

newpointlocs %>%
# mydata %>%
#   add_count(Bird_ID) %>%
  group_by(id) %>% 
  summarise(mov_rate_all = mean(mpm)) -> all_mov_rate

summary(all_mov_rate$mov_rate_all)
mean(all_mov_rate$mov_rate_all)
sd(all_mov_rate$mov_rate_all)
